Active Learning for Level Set Estimation

### 2013-03-22 msthpres.tex
Fix image source style

\documentclass[10pt,mathserif,serif]{beamer}
%\documentclass[10pt,mathserif,serif,draft,handout]{beamer}

@@

@@

\begin{frame}
\begin{center}
Swimmers of Lake Zurich, beware!\\
\vspace{0.2in}
\includegraphics[width=4in]{figures/swimmers.jpg}\\[-0.5em]
{\tiny (Source: Steffen Schmidt / EPA)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\uncover<1->{Swimmers of Lake Zurich, beware!}
\vspace{0.2in}
\begin{columns}[c]
\column{0.4\textwidth}
\uncover<1->{
\minipage[c][0.75\textheight][s]{\columnwidth}
\includegraphics[width=1.7in]{figures/pr.jpeg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}\\
\vfill
\includegraphics[width=1.7in]{figures/bloom.jpg}\\[-0.5em]
{\tiny (Source: Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey)}
\endminipage
}

\column{0.6\textwidth}
\minipage[c][0.75\textheight][s]{\columnwidth}
\uncover<1->{
\small
``The warming waters of one of central Europe's most popular holiday
destinations, Switzerland's Lake Zurich, have created an ideal environment
for a population explosion of algae including \emph{Planktothrix rubescens},
[...]''
\qauth{Scientific American}
}
\vfill
\uncover<2->{
\small
``\emph{Planktotrhix rubescens} can account for half of the total
phytoplankton biomass in Lake Zurich in summer [...]''
\vspace{1em}

@@

\begin{frame}
\begin{center}
\vspace{0.2in}
\only<1>{
\includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}}
\only<2>{
\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}}
\only<3>{
\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}}
\end{center}
\end{frame}

@@

@@

\begin{frame}
\begin{enumerate}
\item bla
\end{enumerate}
\end{frame}

>>>>

\documentclass[10pt,mathserif,serif]{beamer}
%\documentclass[10pt,mathserif,serif,handout]{beamer}

@@

\newcommand{\sig}[2]{%
\begin{tabular}{r}
#1\\[-0.7em]
{\tiny \color{darkgray}\it #2\hspace{0.5em}}
\end{tabular}}

@@

\begin{frame}
\begin{center}
Swimmers of Lake Zurich, beware!\\
\vspace{0.2in}
\sig{\includegraphics[width=4in]{figures/swimmers.jpg}}{Steffen Schmidt / EPA}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\uncover<1->{Swimmers of Lake Zurich, beware!}
\vspace{0.2in}
\begin{columns}[c]
\column{0.4\textwidth}
\uncover<1->{
\sig{\includegraphics[width=1.7in]{figures/pr.jpeg}}{www.limnobotics.ch}\\[1em]
\sig{\includegraphics[width=1.7in]{figures/bloom.jpg}}{Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey}
}
\column{0.6\textwidth}
\minipage[c][0.80\textheight][s]{\columnwidth}
\uncover<1->{
\small
``The warming waters of one of central Europe's most popular holiday
destinations, Switzerland's Lake Zurich, have created an ideal environment
for a population explosion of algae including \emph{Planktothrix rubescens},
[...]''
\qauth{Scientific American}
}
\vfill
\uncover<2->{
\small
``\emph{Planktotrhix rubescens} can account for half of the total
phytoplankton biomass in Lake Zurich in summer [...]''
\vspace{1em}

@@

\begin{frame}
\begin{center}
\vspace{0.2in}
\only<1>{
\sig{\includegraphics[width=2in]{figures/manual.jpg}}{www.limnobotics.ch}
}
\only<2>{
\sig{\includegraphics[width=4in]{figures/boat.jpg}}{www.limnobotics.ch}
}
\only<3>{
\sig{\includegraphics[width=4in]{figures/lake.png}}{www.limnobotics.ch}
}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Up to this point we have assumed a fixed cost per sample
\item<2-> What about the traveling distance between measurements?
\item<3-> Plan ahead:
\begin{itemize}
\item Select a \emph{batch} of sampling locations
\item Connect them using a Euclidean TSP path
\item Traverse the path and collect measurements
\end{itemize}
\end{itemize}

\begin{center}
\color{white}
\includegraphics<1-3>[draft,width=3.78in]{figures/limno_bgape_pp_0_0}
\color{black}
\includegraphics<4>[height=1.8in]{figures/limno_bgape_pp_0_0}
\includegraphics<5>[height=1.8in]{figures/limno_bgape_pp_0_1}
\includegraphics<6>[height=1.8in]{figures/limno_bgape_pp_0_2}
\includegraphics<7>[height=1.8in]{figures/limno_bgape_pp_30_0}
\includegraphics<8>[height=1.8in]{figures/limno_bgape_pp_30_1}
\includegraphics<9>[height=1.8in]{figures/limno_bgape_pp_30_2}
\includegraphics<10>[height=1.8in]{figures/limno_bgape_pp_60_0}
\includegraphics<11>[height=1.8in]{figures/limno_bgape_pp_60_1}
\includegraphics<12>[height=1.8in]{figures/limno_bgape_pp_60_2}
\includegraphics<13>[height=1.8in]{figures/limno_bgape_pp_90_0}
\includegraphics<14>[height=1.8in]{figures/limno_bgape_pp_90_1}
\includegraphics<15>[height=1.8in]{figures/limno_bgape_pp_90_2}
\includegraphics<16>[height=1.8in]{figures/limno_bgape_pp_120_0}
\includegraphics<17>[height=1.8in]{figures/limno_bgape_pp_120_1}
\includegraphics<18>[height=1.8in]{figures/limno_bgape_pp_120_2}
\includegraphics<19>[height=1.8in]{figures/limno_bgape_pp_150_0}
\includegraphics<20>[height=1.8in]{figures/limno_bgape_pp_150_1}
\includegraphics<21>[height=1.8in]{figures/limno_bgape_pp_150_2}
\includegraphics<22>[height=1.8in]{figures/limno_bgape_pp_180_0}
\includegraphics<23>[height=1.8in]{figures/limno_bgape_pp_180_1}
\includegraphics<24>[height=1.8in]{figures/limno_bgape_pp_180_2}
\includegraphics<25>[height=1.8in]{figures/limno_bgape_pp_210_0}
\includegraphics<26>[height=1.8in]{figures/ev_bgape_pp}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Summary
\end{center}
\vspace{-1em}
\begin{itemize}
\item<1-> \acl algorithm:
\begin{itemize}
\item<2-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
\item<3-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
\end{itemize}
\item<4-> Two useful extensions:
\begin{itemize}
\item<5-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
\item<6-> \begin{tabular}{m{5.5cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
\end{itemize}
\item<7-> Look out for algae when swimming in Lake Zurich! =)
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
\large Questions?\\
\vspace{2em}
\sig{\includegraphics[width=3in]{figures/dilbert}}{www.dilbert.com}
\end{center}
\end{frame}
